HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-18 paper/main.tex
edits

We now describe the HUME annotation interface, shown in \figref{fig:interface}. 
%We turn to discuss the interface for collecting human judgements on the semantic units
%of the source, relating to the translation. 
UCCA annotations of the source are done offline,
using the UCCA web application.
%\figref{fig:interface} presents the user interface of HUME. 
The translation appears at the top, and
the source sentence directly below it. Underneath the source sentence appears
its list of semantic units. 
%For each semantic unit, including the one for the
%entire source sentence, there is a textbox, displaying the yield of that unit.
%Information on the category of the unit (e.g., whether it is a Scene, participant etc.).
The user is asked to select a label for each unit,
by clicking the ``A'', ``B'', Green, Orange, or Red buttons to the right of the unit's box.
Note that the UCCA labels are not shown.

@@

\emph{Describe the UCCA annotation}

@@

In order to assess the consistency of the annotation, we measure the Inter-Annotator
Agreement (IAA) using Cohen's Kappa on the multiply-annotated portions of the data.
For German, Polish and Romanian we used two annotators, with a significant overlap
between the sentences they annotated. For Czech we had one main annotator, who
annotated the entire batch, as well multiple secondary annotators, where
each annotated a sub-part of the batch. \oa{i editted it. is what i wrote correct?}

In order to compute Kappa, we consider the annotation task as a classification task on 
nodes, and compute agreement on nodes which have two annotations from different annotators.
We report the overall Kappa, as well as separate Kappas on atomic
nodes (annotated as Red, Orange or Green) and the structural nodes (annotated
as Adequate or Bad). In general there should be little confusion between the two
types of nodes, and in future work the separation between the nodes should be enforced
by the tool\oa{but there may be some disagreement in the margins on what nodes are atomic and
  what are not}. The Kappas are shown in \tabref{tab:iaa}.

\begin{table}[!ht]
\begin{center}
\begin{tabular}{l|cccc}
 & cs & de & pl & ro \\
\hline
Sentences & 181 & 102 & 334 & 217 \\
\hline
All nodes & 4686   & 2793   & 8384   & 5604  \\
Kappa & 0.64   & 0.61   & 0.58   & 0.69  \\
\hline
Atomic nodes & 2982 & 1724 & 5386 & 3570 \\
Kappa & 0.54 & 0.29 & 0.54 & 0.50 \\
\hline
Structural nodes & 1602 & 1040 & 2655 & 1989 \\
Kappa & 0.31 & 0.44 & 0.33 & 0.58 \\
\end{tabular}
\caption{Inter-annotator agreement for the multiply-annotated portions of the data, as
measured by Cohen's Kappa. }
\label{tab:iaa}
\end{center}
\end{table}

@@

\begin{figure}[ht!]
\renewcommand{\tabcolsep}{0pt}
\begin{tabular}{cc}

@@

\begin{figure}[ht!]
\renewcommand{\tabcolsep}{0pt}
\begin{tabular}{cc}

>>>>

\figref{fig:interface} shows the HUME annotation interface.
% We now describe the HUME annotation interface, shown in \figref{fig:interface}. 
% %We turn to discuss the interface for collecting human judgements on the semantic units
% %of the source, relating to the translation. 
% UCCA annotations of the source are done offline,
% using the UCCA web application.
% %\figref{fig:interface} presents the user interface of HUME. 
% The translation appears at the top, and
% the source sentence directly below it. Underneath the source sentence appears
% its list of semantic units. 
% %For each semantic unit, including the one for the
% %entire source sentence, there is a textbox, displaying the yield of that unit.
% %Information on the category of the unit (e.g., whether it is a Scene, participant etc.).
The user is asked to select a label for each source semantic unit,
by clicking the ``A'', ``B'', Green, Orange, or Red buttons to the right of the unit's box.
%Note that the UCCA labels are not shown.

@@

%\XXX{Describe the UCCA annotation}
% ... not enough room or time

@@

In order to assess the consistency of the annotation, we measure the Inter-Annotator
Agreement (IAA) using Cohen's Kappa on the multiply-annotated portions of the data.
For German, Polish and Romanian we used two annotators, with a significant overlap
between the sentences they annotated. For Czech we had the entire batch
annotated by one main annotator and multiple secondary annotators, 
each annotating a sub-part of the batch.

In order to compute Kappa, we consider the annotation task as a classification task on 
nodes, and compute agreement on nodes which have two annotations from different annotators.
We report the overall Kappa, as well as separate Kappas on atomic
nodes (annotated as Red, Orange or Green) and the structural nodes (annotated
as Adequate or Bad).
As expected and confirmed by confusion matrices in \figref{fig:heatmap}, there
is generally little confusion between the two types of nodes.

%In general there should be little confusion between the two
%types of nodes, and in future work the separation between the nodes should be enforced
%by the tool.
%\oa{but there may be some disagreement in the margins on what nodes are atomic and
%  what are not}
%The Kappas are shown in \tabref{tab:iaa}.

\begin{table}[t]
\begin{center}
\begin{tabular}{l|cccc}
 & cs & de & pl & ro \\
\hline
Sentences & 181 & 102 & 334 & 217 \\
\hline
All nodes & 4686   & 2793   & 8384   & 5604  \\
Kappa & 0.64   & 0.61   & 0.58   & 0.69  \\
\hline
Atomic nodes & 2982 & 1724 & 5386 & 3570 \\
Kappa & 0.54 & 0.29 & 0.54 & 0.50 \\
\hline
Structural nodes & 1602 & 1040 & 2655 & 1989 \\
Kappa & 0.31 & 0.44 & 0.33 & 0.58 \\
\end{tabular}
\caption{Inter-annotator agreement for the multiply-annotated portions of the data, as
measured by Cohen's Kappa. }
\label{tab:iaa}
\end{center}
\end{table}

\begin{figure}[t]
\renewcommand{\tabcolsep}{0pt}
\begin{tabular}{cc}

@@

\begin{figure}[t]
\renewcommand{\tabcolsep}{0pt}
\begin{tabular}{cc}

@@
